\documentclass[a4paper, 12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Report DEVELOPMENT OF RELIABLE, SAFE, AND SECURE SOFTWARE}
\author{Andrea Ciccarello}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This report details the work I have done on the Isolette project
\end{abstract}

\tableofcontents

\section{Isolette Control System Requirements}

I worked with the team in order to write every requirements related to the CLT unit in the project,
due to the nature of the ctl requirements we had to collaborate with every team in otder to have a clear
separation of each unit in the project.
Each requirement has been written in strict docs format and has been reviewed by the team.

The requirements are divided in High Level Requirements (HLR) and Low Level Requirements (LLR),
each LLR must have one or more HLR parent (Traceability) and each HLR must have one or more LLR child.
CLT has been build as a state machine, main states are: CTL\_INIT, CTL\_INPUT, CTL\_OPERATION, CTL\_ERROR.

In each state the CTL has handle multiple events and check in order to operate in a safe and secure way.

We have defined 19 Low Level Requirements and 4 main High Level Requirements for the CLT unit

\begin{itemize}
    \item CTL shall control temperature
    \item CTL shall assess system health
    \item CTL shall provide notifications and alarms
    \item CTL shall solicit and respond to user interaction
\end{itemize}

CTL have to interact with every unit of the project, handle correctly self test of the system, report errors to the UI unit.

\section{Assumptions}

I helped writing about Assumptions related to nurses. 
This is the current list available in the project paper (Isolette\_nurse\_assumptions.csv):

\begin{itemize}
    \item Nurses are highly specialized professionals, trained to provide expert care to Infants in intensive care.
    \item Nurses can be trained to use technical devices, including those that are controlled by computers with ordinary user interface elements.
    \item Nurses are not visually or hearing impaired and can interact with ordinary user interface elements such as buttons and keyboards.
    \item Nurses can move Infants as needed.
\end{itemize}

For each assumptions I alswo wrote about the reasons why we have to consider them relevant for the project.


\section{Program Documentation and Doxygen}

I worked on the Doxygen and program documentation, ensuring the correctness of the current README instructions for the generation of the documentation.
I studied how to write Doxygen documentation and provided assistance in using special commands properly. 
I collaborated with the CMAKE team to enable the use of make for generating documentation for Test and System source code; previously, this was only possible with a script. 
I contributed to the current Doxygen guidelines, making multiple commits to ensure the project is up to date with the latest standards.
I delated useless command like @breaf and @par that were misused in the project.
I worked with the Traceability man to ensure a common guidelines for the documentation of the project.

\section{Hardware Abstraction Layer: Isolette and Room Air}

I reimplemented the Hardware Abstraction Layer source code for Isolette Air and Room Air. I addressed issues identified in the mutation analysis and collaborated with the Heater team to establish a common method for handling temperature and heat exchange between heating surfaces and the air.
Isolette and Room air Hardware Abstraction Layer now have 100\% mull Mutation score and MCDC coverage.

\section{Comparison with FAA: Requirements and Study}

I worked with the FAA analysis team to compare the Isolette project with the FAA project report developed by the US government. This analysis was presented to the entire team.

My responsibilities included studying:

\begin{itemize}
    \item The project description of "External Entities" and their specifications:
    \begin{itemize}
        \item Temperature Sensor
        \item Heat Source
        \item Operator Interface
    \end{itemize}
    \item Safety requirements, such as prolonged exposure of infants to unsafe heat or cold, classified as a catastrophic event:
    \begin{itemize}
        \item Thermostat System Function
        \item Regulate Temperature Function
    \end{itemize}
\end{itemize}

I also had to write a report about requirements of the FAA project inside a chapter of the paper.

\section{MISRA C:2012 Compliance}

We started to work on the MISRA C:2012 compliance of the project with the study of the MISRA C:2012 guidelines.
Every MISRA C guideline is classified as either being a “rule” or a “directive”.
A directive is a guideline for which it is not possible to provide the full description necessary to perform a check for compliance.
A rule is a guideline for which a complete description of the requirement has been provided. 
It should be possible to check that source code complies with a rule without needing any other information.

Guidelines can be classified as:
\begin{itemize}
    \item Mandatory: A guideline that must be followed.
    \item Required: A guideline that should be followed.
    \item Advisory: A guideline that is only recommended (can't just ignore them).
\end{itemize}

For each rule we have a brief description, a category, the version which the rule applies to, the scope of the analysis (like Single Translation unit), 
an Amplification (not Mandatory) an Rationale where is explained why the rule is important, a list of examples (not mandatory).

For this project we use Eclair \cite{Eclair} as a tool static analysis tool to check the MISRA C:2012 compliance of the project.

\section{Logging}

I studied the current logging system handled by the Boost library available in the project. 
I wrote a tutorial on this topic, included in an appendix of the project documentation. Additionally, I provided a brief description of the current logging guidelines and assisted in applying them to the project.
I improved the current logging initialization system in the main.cc file with a better handling of the log file and when we have to set the 
severity level of the log system.


\begin{thebibliography}{9}
    \bibitem{latexcompanion} 
    Leslie Lamport.
    \textit{LaTeX: A Document Preparation System}.
    Addison Wesley, 2nd edition, 1994.

    \bibitem{Eclair}
    Bugseng Website
    https://www.bugseng.com/eclair/eclairit

    \bibitem{Doxygen}
    Doxygen Manual
    https://www.doxygen.nl/manual/index.html

\end{thebibliography}

\end{document}
